---
title: "Blockchain and sustainability reporting"
format: html
toc: true
toc-depth: 3
code-fold: false
execute:
  echo: false
  warning: false
  message: false
---

## Sample analysis

Results from this [link](https://www.webofscience.com/wos/woscc/summary/73b4b487-b0e8-4e25-a380-d3e34a86069c-93706080/relevance/1)

Clarivate Analytics WoS

Summarize main results of the bibliometric analysis

```{r}
library(bibliometrix)

M <- convert2df(file = "/Users/e5028514/Desktop/lit_review/textile/blockchain_textile_wos.bib", dbsource = "wos", format = "bibtex")

```

```{r}
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```

Countries collaborating on this set of bibliographic data



```{r}
countries <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(countries, analysis = "collaboration", network = "countries", sep = ";")
net=networkPlot(NetMatrix, n = dim(NetMatrix)[1], Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE,labelsize=0.7,cluster="none")



```


main bibliometric measures

```{r}
# main bibliometric measures
results <- biblioAnalysis(M, sep = ";")
```

summarize main results of the bibliometric analysis

```{r}
#summarize main results of the bibliometric analysis
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
S
```




```{r}
plot_res<-plot(x = results[["MostCitedPapers"]], k = 10, pause = FALSE)

plot_res

```

most frequent cited manuscripts

```{r}
#most frequent cited manuscripts
CR <- citations(M, field = "article", sep = ";")
cbind(CR$Cited[1:10])
```

most frequent cited first authors

```{r}
#most frequent cited first authors
CR <- citations(M, field = "author", sep = ";")
cbind(CR$Cited[1:10])
```

most frequent local cited authors

```{r}
#most frequent local cited authors
CR <- localCitations(M, sep = ";")
CR$Authors[1:10,]
```

most frequent local cited papers

```{r}
CR$Papers[1:10,]
```

Authors’ Dominance ranking

```{r}
#Authors’ Dominance ranking
DF <- dominance(results, k = 10)
DF
```

H index for *ALOFI A*
```{r}
#H index
indices <- Hindex(M, field = "author", elements="AGRAWAL TK", sep = ";", years = 10)
```

AGRAWAL TK's impact indices

```{r}
# AGRAWAL TK impact indices:
indices$H
```

Citation list

```{r}
indices$CitationList
```


Top-Authors’ Productivity over the Time

```{r}
#Top-Authors’ Productivity over the Time
authors=gsub(","," ",names(results$Authors)[1:10])

indices <- Hindex(M, field = "author", elements=authors, sep = ";", years = 50)

indices$H
```


Top local authors and Author's productivity per year

```{r}
topAU <- authorProdOverTime(M, k = 10, graph = TRUE)

## Table: Author's productivity per year
head(topAU$dfAU)

```

Conceptual structure map of a scientific field (based on Author's keywords)


```{r}
cs <- conceptualStructure(M, field = "DE", method = "MCA", quali.supp = NULL, quanti.supp = NULL, minDegree = 2, k.max = 5, stemming = FALSE, labelsize = 10, documents = 50)
```

