---
title: "DSM-5 Gaming Disorder Taskforce"
author: "Dr Maria Prokofieva"
format: html
toc: true
toc-depth: 3
code-fold: false
execute:
  echo: false
  warning: false
  message: false
---

## Setup

**Keywords for DSM-5 GD Taskforce**

-   Internet Gaming Disorder

-   Gaming Disorder

-   Problematic Gaming

-   Problematic Video Gaming

-   Video Game Addiction

-   Game Addiction

-   Problematic Online Gaming

-   Online Game Addiction

-   Pathological Video Gaming

-   Pathological Gaming

**Exclusion criteria for ML network analysis**: 

anything published before 2013

**Article Databases to review**: 

• Scopus https://www.scopus.com/ (only first 2,000 entries are allowed for export, different sorting approach is used to generated full set)

• PubMed https://pubmed.ncbi.nlm.nih.gov/

• Science Direct X

• ProQuest 

• Ebsco 

• PyschINFO 

• Gale


*Question*: research articles and/or review articles?

## Preliminary results

#### Summarize main results of the bibliometric analysis (Scopus)
```{r}
library(bibliometrix)
library(tidyverse)

files_bib<-list.files(
  path="/Users/e5028514/Desktop/lit_review/database_import/", 
  pattern="^scopus*",
  full.names=TRUE
)

bib_data<- lapply(files_bib, function(file){
  convert2df(file, dbsource = "scopus", format = "bibtex")
})
M <- dplyr::bind_rows(bib_data)
M<-M%>% distinct(url, .keep_all=TRUE)

# main bibliometric measures
results <- biblioAnalysis(M, sep = ";")
summary(results, k=10, pause=F, width=130)

```

```{r}
plot(x=results, k=10, pause=F)
```
### Most Cited References

```{r}
CR <- citations(M, field = "article", sep = ";")
cbind(CR$Cited[1:20])
```


## The Intellectual Structure of the field - Co-citation Analysis

### Article (References) co-citation analysis

```{r}
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")
net=networkPlot(NetMatrix, n = 50, Title = "Co-Citation Network", type = "fruchterman", size.cex=TRUE, size=20, remove.multiple=FALSE, labelsize=1,edgesize = 10, edges.min=5)
```


### Co-word Analysis through Keyword co-occurrences


The plot uses the main 50 cited references and applies the [Fruchterman-Reingold Algorithm](https://en.wikipedia.org/wiki/Force-directed_graph_drawing) for network generation


```{r}
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```


Descriptive analysis of Article co-citation network characteristics


```{r}
netstat <- networkStat(NetMatrix)
summary(netstat,k=10)
```
### Journal (Source) co-citation analysis

```{r}
M=metaTagExtraction(M,"CR_SO",sep=";")
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "sources", sep = ";")

net=networkPlot(NetMatrix, n = 20, Title = "Co-Citation Network", type = "auto", size.cex=TRUE, size=15, remove.multiple=FALSE, labelsize=1,edgesize = 10, edges.min=5)
```
Descriptive analysis of Journal co-citation network characteristics

```{r}
netstat <- networkStat(NetMatrix)
summary(netstat,k=10)
```

## Historiograph - Direct citation linkages


```{r}
histResults <- histNetwork(M, sep = ";")

```

```{r}
options(width = 130)
net <- histPlot(histResults, n=20, size = 5, labelsize = 4)
```

## The conceptual structure - Co-Word Analysis

### Co-word Analysis through Keyword co-occurrences

The network layout is generated using the Fruchterman-Reingold Algorithm)

```{r}
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
net=networkPlot(NetMatrix, normalize="association", n = 50, Title = "Keyword Co-occurrences", type = "fruchterman", size.cex=TRUE, size=20, remove.multiple=F, edgesize = 10, labelsize=5,label.cex=TRUE,label.n=30,edges.min=2)
```

Descriptive analysis of keyword co-occurrences network characteristics


```{r}
netstat <- networkStat(NetMatrix)
summary(netstat,k=10)

```

### Co-word Analysis through Correspondence Analysis

```{r}
suppressWarnings(
CS <- conceptualStructure(M, method="MCA", field="ID", minDegree=15, clust=5, stemming=FALSE, labelsize=15,documents=20)
)
```


## Thematic Map

Co-word analysis is used to identify clusters of keywords based on [this](https://www.mdpi.com/2071-1050/14/6/3643) . Clusters are used as themes and their characteristics (e.g. density and centrality) are used in classifying themes and mapping as two-dimensional diagram.

The result is a thematic map which is an intuitive tool to present themes for further analysis based on  the quadrant in which themes are placed: 

(1) upper-right quadrant: motor-themes; 

(2) lower-right quadrant: basic themes; 

(3) lower-left quadrant: emerging or disappearing themes; 

(4) upper-left quadrant: very specialized/niche themes.

```{r}
Map=thematicMap(M, field = "ID", n = 250, minfreq = 4,
  stemming = FALSE, size = 0.7, n.labels=5, repel = TRUE)
plot(Map$map)
```

Cluster description

```{r}
Clusters=Map$words[order(Map$words$Cluster,-Map$words$Occurrences),]
library(dplyr)
```

## The social structure - Collaboration Analysis

Collaboration network analysis evaluates how authors / institutions / countries relate to others in a specific field of research.

Such analysis include generation of a co-author network to evaluate distinct groupings, e.g. regular study groups, hidden groups of scholars, and pivotal authors. 

Further analysis includes generation of the collaboration network which links relevant institutions  in the field and uncover their relations.

### Author collaboration network

```{r}
NetMatrix <- biblioNetwork(M, analysis = "collaboration",  network = "authors", sep = ";")
net=networkPlot(NetMatrix,  n = 50, Title = "Author collaboration",type = "auto", size=10,size.cex=T,edgesize = 3,labelsize=1)
```

Descriptive analysis of author collaboration network characteristics

```{r}
netstat <- networkStat(NetMatrix)
summary(netstat,k=15)
```


Institutional collaboration

```{r}
NetMatrix <- biblioNetwork(M, analysis = "collaboration",  network = "universities", sep = ";")
net=networkPlot(NetMatrix,  n = 50, Title = "Institutional collaboration",type = "auto", size=4,size.cex=F,edgesize = 3,labelsize=1)
```

Descriptive analysis of edu collaboration network characteristics


```{r}
netstat <- networkStat(NetMatrix)
summary(netstat,k=15)
```


Countries collaborating on this set of bibliographic data

```{r}
M <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "collaboration",  network = "countries", sep = ";")
net=networkPlot(NetMatrix,  n = dim(NetMatrix)[1], Title = "Country collaboration",type = "circle", size=10,size.cex=T,edgesize = 1,labelsize=0.6, cluster="none")
```

Descriptive analysis of country collaboration network characteristics

```{r}
netstat <- networkStat(NetMatrix)
summary(netstat,k=15)
```
