---
title: "lit review - test"
format: html
toc: true
toc-depth: 3
code-fold: false
execute:
  echo: false
  warning: false
  message: false
---

## Sample analysis


#### Summarize main results of the bibliometric analysis
```{r}
library(bibliometrix)

M <- convert2df(file = "data/p1.bib", dbsource = "isi", format = "bibtex")

# main bibliometric measures
results <- biblioAnalysis(M, sep = ";")

#summarize main results of the bibliometric analysis
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
S
```

Plot

```{r}
plot_res<-plot(x = results, k = 10, pause = FALSE)

plot_res
```

most frequent cited manuscripts

```{r}
#most frequent cited manuscripts
CR <- citations(M, field = "article", sep = ";")
cbind(CR$Cited[1:10])
```

most frequent cited first authors

```{r}
#most frequent cited first authors
CR <- citations(M, field = "author", sep = ";")
cbind(CR$Cited[2:10])
```

most frequent local cited authors

```{r}
#most frequent local cited authors
CR <- localCitations(M, sep = ";")
CR$Authors[1:10,]
```

most frequent local cited papers

```{r}
CR$Papers[1:10,]
```

Authors’ Dominance ranking

```{r}
#Authors’ Dominance ranking
DF <- dominance(results, k = 10)
DF
```

H index for *BENETOLI A*
```{r}
#H index
indices <- Hindex(M, field = "author", elements="BENETOLI A", sep = ";", years = 10)
```

Bornmann's impact indices

```{r}
# Bornmann's impact indices:
indices$H
```

Citation list

```{r}
indices$CitationList
```


Top-Authors’ Productivity over the Time

```{r}
#Top-Authors’ Productivity over the Time
authors=gsub(","," ",names(results$Authors)[1:10])

indices <- Hindex(M, field = "author", elements=authors, sep = ";", years = 50)

indices$H
```


Top local authors and Author's productivity per year

```{r}
topAU <- authorProdOverTime(M, k = 10, graph = TRUE)

## Table: Author's productivity per year
head(topAU$dfAU)




```
